Lesson 3
========================================================

***

### What to Do First?
Notes:
data in the good directory
***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
pf <- read.csv('data/pseudo_facebook.tsv',sep = '\t' )
names(pf)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
#install.packages('ggplot2')
library(ggplot2)

#qplot(x = dob_day,data = pf) +scale_x_continuous(breaks=1:31)
#or 
ggplot(aes(x = dob_day), data = pf) +
  geom_histogram(binwidth = 1) +
  scale_x_continuous(breaks = 1:31)
```


***

#### What are some things that you notice about this histogram?
Response:
There's surprisingly too many people born on the 1st of any month
***

### Moira's Investigation
Notes:
ppe underestimate audience
***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:first post 

#### How many of your friends do you think saw that post?
Response:3

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:10

***

### Perceived Audience Size
Notes:???

***
### Faceting
Notes:
facet_wrap(~<var>) breaks the plot into several columns given variable <var> 
facet_grid(var1~var2) similar but vertical then horizontal 
```{r Faceting}
ggplot(data = pf, aes(x = dob_day))+
  geom_histogram(binwidth = 1) +
  scale_x_continuous(breaks = 1:31)+
  facet_wrap(~dob_month)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:
01/01 is surprisingly large
***

### Be Skeptical - Outliers and Anomalies
Notes:
There are *many* different sorts of outliers
***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:
Bad data about extreme cases

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(data = pf, aes(x = friend_count)) +  geom_histogram(binwidth = 30)
```

#### How is this plot similar to Moira's first plot?
Response:
it decreases with a long tail, with users having up to 5k friends
***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
ggplot(data = pf, aes(x = friend_count)) +  
  geom_histogram(binwidth = 30) +
  scale_x_continuous(limits = c(0, 1000))
# equivalent qplot: qplot(x,friend_count, data = pf, xlim = c(0,1000))
```

### Exploring with Bin Width
Notes:
moira: people tend to choose 10, 20, 25, 50 as answers, so need to check the binwidth!!
***

### Adjusting the Bin Width
Notes:
look at the binwidth argument
also possible to adjuts the ticks with the `breaks` argument

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:
use subset command in data = subset(pf, <condition>)
also we can use the na.omit() function
exp:
```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf, !is.na(gender)),binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:
summary `by`
```{r Statistics \'by\' Gender}
by(pf$friend_count,pf$gender,summary)
```

#### Who on average has more friends: men or women?
Response:
M
#### What's the difference between the median friend count for women and men?
Response:
+ 22 for men
#### Why would the median be a better measure than the mean?
Response:
The mean is affected by the larger values (4000, 5000) which correspond to few people
***

### Tenure (days using fb)
Notes:

```{r Tenure}
qplot(x = tenure, data = pf,
      color = I('black'), fill = I('#099DD9'),
  breaks = seq(0, 3650, 365)) 
```


***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(x = tenure/365, data = pf,
      xlab = 'nb of years on fb',
      ylab = 'nb of users in sample',
      color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(breaks = seq(1,7,1),lim = c(0,7))
```

***

### User Ages
Notes:
small binwidths -> good for spotting weird stuff in the data
```{r User Ages}
qplot(x = age, data = pf,
      binwidth = 1,
      xlab = 'age',
      ylab = 'nb of users in sample',
      color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(breaks = seq(0,112,4),lim = c(0,112))
```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:
log useful
***

### Transforming Data
Notes:
Engagement variables:
 use sqrt or log /log2/log10 ... 
```{r}
summary(log10(pf$friend_count + 1 ))

summary(sqrt(pf$friend_count + 1 ))
```

*Multiple plots*:  `install.packages("gridExtra")`

grid extra: (http://lightonphiri.org/blog/ggplot2-multiple-plots-in-one-graph-using-gridextra) 
play iwth scales: (http://docs.ggplot2.org/current/scale_continuous.html)

```{r}
library(gridExtra)
p1 = qplot(x = log10(friend_count), data = pf,
      color = I('black'), fill = I('#099DD9'))
    #+   scale_x_log10()
    + scale_x_continuous(breaks = 1:10)
p2 = qplot(x = sqrt(friend_count), data = pf,
      color = I('black'), fill = I('#099DD9'))
     +   scale_x_sqrt() 
p3 = qplot(x = friend_count, data = pf,
      color = I('black'), fill = I('#099DD9'))
grid.arrange(p1, p2,p3 , ncol=1)
```
Or with ggplot syntax:

```{r}
p1 = ggplot(aes(x = friend_count),data = pf) +
  geom_histogram()
p2 = p1 + scale_x_log10()
p3 = p1 + scale_x_sqrt()
grid.arrange(p1, p2,p3 , ncol=1)
```

###Another type of plots (curve)
aka frequency polygons : 
keyword:  `geom = 'freqpoly'`

```{r}
qplot(x = friend_count , data = subset(pf,!is.na(gender)), 
      binwidth = 10, geom = 'freqpoly', color = gender) + 
  scale_x_continuous(lim = c(0,1000), breaks = seq(0,1000,50))
```


###Playing with the y scale

we can vary the y *range*   by using `y = ..count../sum(..count..)`

```{r}
qplot(x = friend_count, y = ..count../sum(..count..) , data = subset(pf,!is.na(gender)),
      xlab = 'FriendCount',
      ylab = 'Proportion of users with that friend count',
      binwidth = 10, geom = 'freqpoly', color = gender) + 
  scale_x_continuous(lim = c(0,1000), breaks = seq(0,1000,50))
```
 



***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}

```

***


### Frequency Polygons

```{r Frequency Polygons}

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}

```


***

### Box Plots
Notes:

```{r Box Plots}

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!